---
title: "Analysis"
author: "Anne Christine Vig Jensen"
date: "`r Sys.Date()`"
output: html_document
---
 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "~/Desktop/bachelor/onde_bachelor/checking_timing") # set working directory 
  
pacman::p_load(lmerTest)
set.seed(420)
```
 
#### RQ 1

RQ 1: *Is overall coordination stability lower in conditions with subgroups compared to conditions with no subgroups?*

Model 1: Predicting the coefficient of variation (cv) based on whether a condition has subgroups or not 

Model syntax: 

$$ \textit{coeffeicient of variation} \sim subgroup + (1 \mid group )$$

```{r RQ1 - overall cv}
RQ1_overall <- lmerTest::lmer(cv ~ subgroup_present + (1 | group_id), combined_data)

summary(RQ1_overall)
anova(RQ1_overall) 
head(combined_data)
```

#### RQ 2

RQ 2: *Is agency generally experienced as more shared for members of subgroups compared to individuals in the same condition?* 
+ 
*If a subgroup member has higher coordination stability, does that member report more shared agency with their partner?*

Model 2: Shared agency is predicted by whether a participant is in a subgroup + the coordination stability with random intercept for each group 

Syntax: 
$$\textit{shared agency} \sim \textit{subgroup member} + cv + (1 \mid  group)$$
```{r}
combined_data_RQ2 <- combined_data %>% 
  filter(subgroup_present == 1)

RQ2 <- lmerTest::lmer(shared ~ is_a_subgroup_member + cv + (1 | group_id), combined_data_RQ2)
R32 <- lmerTest::lmer(control ~ is_a_subgroup_member + cv + (1 | group_id), combined_data_RQ2)

summary(RQ2)
anova(RQ2) # converts model into type III anova - is there a difference between the means of each variable rather than is there a difference between each intercept 
```

