---
title: "Analysis"
author: "Anne Christine Vig Jensen"
date: "`r Sys.Date()`"
output: html_document
---
 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "~/Desktop/bachelor/onde_bachelor/data_processing") # set working directory 
  
pacman::p_load(lmerTest, tidyverse, performance, effects)
set.seed(420)
```

```{r}
setwd("~/Cognitive_Science/Bachelor/Bachelor2025/data_processing")
data <- read.csv("data.csv")
```

 
#### RQ 1

RQ 1: *Is overall coordination stability lower in conditions with subgroups compared to conditions with no subgroups?*

Model 1: Predicting the coefficient of variation (cv) based on whether a condition has subgroups or not 

Model syntax: 

$$ \textit{coeffeicient of variation} \sim subgroup + (1 \mid group )$$

```{r RQ1 - overall cv}

data_new <- data %>% 
  filter(condition != "231" & condition != "312") 

RQ1_overall_new <- lmerTest::lmer(cv ~ subgroup_present + (1 | group_id), data_new)

RQ1_overall <- lmerTest::lmer(cv ~ subgroup_present + (1 | group_id), data)

summary(RQ1_overall_new)
print("old")
summary(RQ1_overall)
print("anova")
anova(RQ1_overall) 
print("r2")
r2_nakagawa(RQ1_overall)
```



```{r}



combined_data %>% 
  ggplot(aes(x = subgroup_present, y = cv)) +
  geom_violin(fill = "skyblue") +
  #geom_errorbar(aes(ymin = cv - error, ymax = cv + error), width = 0.2) +
  labs(x = "Subgroup present", y = "CV Value", title = "Coefficient of variation by condition") +
  theme_minimal()

ggsave("~/Cognitive_Science/Bachelor/Bachelor2025/data_processing/RQ1_plot.jpg")

?geom_bar
```


```{r}
RQ1.Fixed<-effect(c("subgroup_present"), RQ1_overall,
                           xlevels=list(subgroup_present=seq(0,1,1)))

# You have to convert the output to a dataframe
RQ1.Fixed<-as.data.frame(RQ1.Fixed)

y_min <- mean(combined_data$cv)-sd(combined_data$cv)*2
y_max <- mean(combined_data$cv)+sd(combined_data$cv)*2
#y_min <- mean(combined_data$shared)-sd(combined_data$shared)*2
#y_max <- mean(combined_data$shared)+sd(combined_data$shared)*2



RQ1.Fixed.Plot <-ggplot(data = RQ1.Fixed, aes(x = subgroup_present, y =fit))+
  coord_cartesian(xlim=c(0, 1),ylim = c(y_min, y_max))+ 
  geom_line(size=1)+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se),alpha=.2)+
  geom_point()+
  xlab("Subgroup_present")+
  ylab("CV")+
  #scale_color_manual(values=c("blue", "red"))+
  #scale_fill_manual(values=c("blue", "red"))+
  theme_bw()+
  theme(text=element_text(face="bold", size=12),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        panel.border = element_rect(fill = NA, colour = "NA"),
        axis.line = element_line(size = 1, colour = "grey80"),
        legend.title=element_blank(),
        legend.position = c(.2, .92))
RQ1.Fixed.Plot

```



#### RQ 2

RQ 2: *Is agency generally experienced as more shared for members of subgroups compared to individuals in the same condition?* 
+ 
*If a subgroup member has higher coordination stability, does that member report more shared agency with their partner?*

Model 2: Shared agency is predicted by whether a participant is in a subgroup + the coordination stability with random intercept for each group 

Syntax: 
$$\textit{shared agency} \sim \textit{subgroup member} + cv + (1 \mid  group)$$
```{r}
combined_data$sub <- factor(combined_data$is_a_subgroup_member,
                        levels = c(0,1),
                        labels = c("Loner", "Subgroup"))

combined_data_RQ2 <- combined_data %>% 
  filter(subgroup_present == 1)


RQ2 <- lmerTest::lmer(shared ~ sub + cv + (1 | group_id), combined_data_RQ2)
R32 <- lmerTest::lmer(control ~ is_a_subgroup_member + cv + (1 | group_id), combined_data_RQ2)

summary(RQ2)
anova(RQ2) # converts model into type III anova - is there a difference between the means of each variable rather than is there a difference between each intercept 


summary(RQ2)
print("anova")
anova(RQ2) 
print("r2")
r2_nakagawa(RQ2)
```
```{r}
ranef(RQ2)
r2_nakagawa(RQ2)
```



```{r}
pacman::p_load(effects)

#Model.6<-lmer(HappyPercent ~Social*TimeStep
#                   +(1+Social*TimeStep|Subject),  
#                   data=HappyData, REML=FALSE)
#summary(Model.6, correlations=FALSE)

#ranef(Model.6)

Final.Fixed<-effect(c("sub*cv"), RQ2,
                           xlevels=list(cv=seq(0,1,0.1)))

# You have to convert the output to a dataframe
Final.Fixed<-as.data.frame(Final.Fixed)

x_min <- mean(combined_data$cv)-sd(combined_data$cv)*2
x_max <- mean(combined_data$cv)+sd(combined_data$cv)*2
y_min <- mean(combined_data$shared)-sd(combined_data$shared)*2
y_max <- mean(combined_data$shared)+sd(combined_data$shared)*2

Final.Fixed.Plot <-ggplot(data = Final.Fixed, aes(x = cv, y =fit, group=sub))+
  coord_cartesian(xlim=c(x_min, x_max),ylim = c(y_min, y_max))+ 
  geom_line(aes(color=sub), size=1)+
  geom_ribbon(aes(ymin=fit-se, ymax=fit+se,fill=sub),alpha=.2)+
  xlab("CV")+
  ylab("Shared\nAgency")+
  scale_color_manual(values=c("blue", "red"))+
  scale_fill_manual(values=c("blue", "red"))+
  theme_bw()+
  theme(text=element_text(face="bold", size=12),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        panel.border = element_rect(fill = NA, colour = "NA"),
        axis.line = element_line(size = 1, colour = "grey80"),
        legend.title=element_blank(),
        legend.position = c(.2, .92))
Final.Fixed.Plot

setwd("~/Cognitive_Science/Bachelor/Bachelor2025/data_processing")

ggsave("~/Cognitive_Science/Bachelor/Bachelor2025/data_processing/RQ2_plot_ver2.jpg")
```

